Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-08 WRITEUP/ms.tex
write some more

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field. in any case, we should compress the information, by having a less figures showing multplie cuts (e.g. 3 of them by using thinner lines should suffice in conveying the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.88}.png}
    \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_1.47}.png}
\caption{
Continued.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_2.45}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_4.08}.png}
\caption{
Continued.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_6.81}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_11.36}.png}
\caption{
Continued.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_18.96}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_31.62}.png}
\caption{
Continued.}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the $r_{\rm 200}$ dark matter radius is $\sim$15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.

@@

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure from velocity dispersion, second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS vanishes and the equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere, and we can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to the scaling in one of the Larson's relations (linewidth-size),
and can re-written in the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
For a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsubsection{Single Snapshots: Larson's Relations and Virial Parameter}  \label{sec:singless}

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
The virial parameter of the MC identified in (the densest region of) the main disk of \flower
indicate that the MC itself is gravitationally unbound.

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with cloud sizes on the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally stable structures, which are supported by
turbulence and rotation on large scales.

We also identify MCs in the satellite galaxies of \flower. These MCs
tend to have lower velocity dispersions compared to those of \flower which are more comparable
to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
These MCs in the satellite galaxies also have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely collapsing structures.
Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter,
the MCs of the satellite galaxies of
\flower are close to being in virial equilibrium
and are not supported against collapse by external pressure. % are bound

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase(bottom) and
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds without massive \SF ($<$10\,\Msun) 
in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
Pipe Nebula) and those with massive \SF in the Milky Way, \citet{Kauffmann10c} find a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
with visual extinction of $A_V$\eq4\,mag. This may suggest that xyzxyz.
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase.

@@

\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}

\AP{select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA and the ngVLA 
will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field; additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter ``virial radius'' at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

@@

\subsubsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to the scaling in one of the Larson's relations (linewidth-size)
and can be re-written in the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsubsection{Single Snapshots}  \label{sec:singless}

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound, and is supported/confined 
by turbulence and rotation on large scales.
% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with cloud sizes on the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
These

We also identify MCs in the satellite galaxies of \flower. These MCs
tend to have lower velocity dispersions compared to those of \flower which are more comparable
to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
These MCs in the satellite galaxies also have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely collapsing structures.
Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter,
the MCs of the satellite galaxies of
\flower are close to being in virial equilibrium and are unlikely supported against collapse by external pressure.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
The V-shaped dashed lines show locii along which the given external pressures
are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds without massive \SF ($<$10\,\Msun) 
in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
Pipe Nebula) with those with massive \SF in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase.

@@

\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
of finite thickness $h$
is described by:
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
The first term on the RHS describes rotation support, second term describes self-gravity, and
the third term describes pressure support.
The epicyclic frequency is defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
\label{eqn:kappa}
\end{equation}
% \kappa\propto\Omega
One can then define the so-called Toomre-Q parameter/criterion for stability as
\begin{equation}
Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
\label{eqn:Q}
\end{equation}
We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
\begin{equation}
\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
\end{equation}
Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
and fragmentation can happen
(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
satellite galaxies and stellar feedback).
That is, local fragmentation takes place when gravity overcomes pressure support
from turbulence (thermal is small here) and shearing of differential rotation.

In the limit of a thin rotating disk, rotation can help stabilizes
self-gravitational contraction for wavelengths greater than the Toomre length:
\begin{equation}
\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
\end{equation}
yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
which sets the ``upper limit'' to which MCs can form in a shearing disk.
